%% start of file `cv.tex'.
%% Chris Borins CV ~ Aug 2023
%%
%% Adapted from moderncv template.tex
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')


% moderncv themes
\moderncvstyle{banking}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% adjust the page margins
\usepackage[scale=0.85]{geometry}

% personal data
\firstname{Christina}
\familyname{Borins}
% \address{123 Fake St.}{Stanford, California 94305}

\mobile{+1~(555)~555~5555}
\email{christina.borins@gmail.com}
\homepage{chrissyelie.com}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Production and Artist Experience}

\cventry
  {New York, NY}
  {XR ARTIST MEMBER}
  {ONX Studio}
  {2023 - Present}{}
  {Member of the accelerator program with the 1991 VR documentary. Selected to join based on proven experience in the XR space as well as transformative artistic vision. Based mostly in NYC and LA, members of ONX Studio are each working on a major project that will be developed, produced, and/or presented at ONX. The ONX Studio is founded in partnership by the Onassis Foundation and NEW INC.}

\cventry
  {New York, NY / Toronto, Canada}
  {VR DIRECTOR}
  {VR Documentary “1991”}
  {2018 - Present}{}
  {Co-directing a VR documentary about the affects of the USSR’s collapse on Central Asia. Developing the script and story with the immersive best practices for in-headset and in the physical set.
  }

\cventry
  {Multi-city}
  {Creative Technical Producer / XR Consultant / Interactive Director}
  {CeB Media}
  {2016 - Present}{}
  {Contract work in a variety of specialties including video editing,
  audio editing, producing and directing. Works produced for
  a number of formats including, screen, HMD, live performance,
  and physical installation. Clients: SFMOMA, Dolby Digital, National Film Board of Canada,
  Stanford University, 42 Entertainment, Make A Film Foundation,
  Inclusive Media and Design, New York University, and 2n}

\cventry
  {Toronto, Canada}
  {VR PRODUCER}
  {HOO KOO E KOO}
  {Jan 2022 - Aug 2022}{}
  {}

\cventry
  {New York, NY / Toronto, Canada}
  {SENIOR CREATIVE TECHNICAL PRODUCER}
  {A\_DA}
  {Jun 2021 - Jan 2022}{}
  {Produced experiential and digital projects on a variety platforms. Overseeing internal and external teams to ensure delivery on project milestones and ensuring high value outcomes. Manage software development vendors, tracking work progress and managing the flow of communication between creative and external development teams on multiple VR/AR, web, native applications, and immersive installations/experiences. Worked in collaboration with Microsoft AI for Cultural Heritage project in collaboration with the Greek Government.}
\cventry
  {Jan 2021 - Jun 2021}
  {CREATIVE TECHNICAL PRODUCER}
  {}
  {}{}
  {Managed and produced to development of multiple Web3 climate change-themed audiovisual installations in collaboration with musicians for Undercurrent art exhibition in New York.}

\cventry
  {Nov 2018 - Dec 2020}
  {CREATIVE TECHNICAL PRODUCER}
  {Listen}
  {New York, NY}{}
  {Produced and maintained many interactive and experiencial installations and projects. Projects were in collaboration with Microsoft AI for Culture for high value stakeholders and artists like Muse, Bob Gale, Sol LeWitt, Halo/343 Industries, and many others.}

  \cventry
  {2017}
  {PRODUCER / DIRECTOR}
  {SFMOMA}
  {San Francisco, CA}{}
  {Captured SFMOMA Sountracks Exhibition and created a 360 experience and with ambisonic audio that is hosted on their digital platform.}
  
  \cventry
  {2017}
  {CREATIVE PRODUCER \& CREATOR, VR RESEARCHER}
  {Adobe}
  {San Francisco, CA}{}
  {Adobe Design Residency to explore the edges of the VR medium so the team could be better informed in their VR tooling explorations.}

  \cventry
  {Mar 2016 - Aug 2016}
  {PROGRAM MANAGER, SALES ENABLEMENT}
  {Mixpanel}
  {San Francisco, CA}{}
  {Designed, developed, and managed sales learning initiatives, for on-site and distance learning classes, to drive readiness, productivity and efficiency within the sales team. 
  Partnered with the Sales Engineering team to build and maintain the Competitive Intelligence Program. Continual monitoring of the competitive landscape and industry trends to create briefs of competitive releases and supportive ongoing competitive intel education such that curriculum adjustments and delivery mechanisms were timely and relevant to the various audiences supported at the company.}
\cventry
  {Mar 2015 - Feb 2016}
  {PROGRAM COORDINATOR, SALES ENABLEMENT}
  {}
  {}{}
  {Supported the Sales Enablement team in the development of product educational materials including one pagers of all Mixpanel's product offerings. 
  Coordinated and facilitated the monthly on-boarding program for new hire classes ranging from 8-20 new employees. Restructured and optimized the organization of existing documentation and new processes for both the Sales and Sales Enablement team. 
  Assisted with the planning and execution of internal sales and marketing events.}


\section{Academic Experience}
\cventry
  {Fall 2020}
  {INSTRUCTOR}
  {New York University, Tisch School of the Arts, 
  New York, NY}{}
  {}{}{}
  {Taught approaches to live performamce using immersive and XR technologies in the Brandan Bradley Integrative Technology Lab}

\cventry
  {2020-2021}
  {IN-HOUSE AGENCY TRAINING}
  {Listen \& A\_DA}{}
  {}{}{}
  {Taught multiple sessions on approaches to using technology in immersive experiences}

\cventry
  {2016}
  {SALES ENABLEMENT \& TRAINER}
  {Mixpanel}{}
  {}{}{}
  {Designed, developed, and managed sales learning initiatives, for on-site and distance learning classes, to drive readiness, productivity and efficiency within the sales team.}
  
\section{Education}

\cventry
  {2016 - 2018}{MPS}
  {New York University}{New York, NY}
  {\textit{Masters of Professional Studies}}
  {Two year masters program at \textit{Tisch School of the Arts, Interactive Telecommunications Program (ITP)}.  Studies include Focused on interactive storytelling in installation formats, XR and
  360° production, and site-based installation art. \\\textit{Recipient of the Tisch School of the Arts Scholarship }}

\cventry
  {2005 - 2009}
  {Honors BSc.}
  {University of Toronto}
  {Toronto, Ontario}
  {\textit{Cellular \& Human Biology}}
  {Major in Human Biology and a minor in Environmental and Conservation Sciences}

  \section{Awards and Accomplishments}
\cventry
  {}{OCAD University}
  {OCAD University Medal in Integrated Media}
  {May 2012}{}
  {Top accolade given to one student from each department at time of graduation}
\cventry
  {}{Stanford Arts Institute}
  {Denning Family Fellowship in Fine Arts}
  {March 2012}{}{}
\cventry
  {}{OCAD University}
  {Project 31 Integrated Media Faculty Scholarship}
  {May 2011}{}{}
\cventry
  {}{OCAD University}
  {DFI Award}
  {May 2010}{}{}
\cventry
  {}{OCAD University}
  {InterAccess Media Prize}
  {May 2010}{}{}

\section{Guest Speaking, Lectures, Conferences}
\cventry
  {Online}
  {Discussing "1991", a virtual reality documentary}
  {XLive: Metamersive}
  {July 2022}{}
  {}
\cventry
  {San Francisco}
  {Guest Speaker discussing creative appraoches and design of "1991", a VR documentary}
  {California College of the Arts}
  {Sept 2022}{}
  {}
\cventry
  {Cannes, France}
  {VR Panelist: "Who is afraid of VR? - Can VR replace traditional film?“}
  {Marche du Film, Next Conference at Cannes Film Festival}
  {May 2018}{}
  {}

% \cventry
%   {San Francisco, USA}
%   {Would a sample at any other rate sound as sweet}
%   {ForwardJS 3}
%   {July 2015}{}
%   {https://www.youtube.com/watch?v=6a1iOfyn5e8}
% \cventry
%   {Semiahmoo, USA}
%   {It's not me it's you: on the fallibility of large systems}
%   {CascadiaFest}
%   {July 2015}{}
%   {https://www.youtube.com/watch?v=47XMs6pcf7w}
% \cventry
%   {Amelia Island, USA}
%   {Would a sample at any other rate sound as sweet}
%   {JSConf US}
%   {May 2015}{}
%   {https://www.youtube.com/watch?v=gmQ1kcj8Q2k}
% \cventry
%   {Karlruh, Germany}
%   {From Faust to WebAudio}
%   {Linux Audio Conference}
%   {May 2014}{}
%   {http://lac.linuxaudio.org/2014/recordings/day2/myles\_borins\_360p.webm}

\section{Advisement and Mentorship Experience}
\cventry
  {New York, NY}
  {MPS Interactive Telecommunications Program at NYU Tisch School of the Arts}
  {New York Universtiy, Graduate Thesis Review Committee}
  {2019-2021}{}
  {}

\cventry
  {New York, NY}
  {Early Advisement on user experience and casting for festival touring VR experience.}
  {Stay Alive My Son, Narrative VR Experience}
  {2016}{}
  {Premiered at Venice Film Festival 2022}



\begin{thebibliography}{9}

\bibitem{linuxaudio}
  M Borins,
  \textit{From faust to web audio: Compiling faust to javascript using emscripten},
  Linux Audio Conference Proceedings,
  2014.

\bibitem{satellite}
  E Berdahl, S Salazar, M Borins
  \textit{Embedded Networking and Hardware-Accelerated Graphics with Satellite CCRMA.},
  NIME Proceedings,
  2013.

\bibitem{blackbox}
  R Michon, M Borins, D Meisenholder
  \textit{The Black Box.},
  NIME Proceedings,
  2013.

\bibitem{ocad}
  M Page, N Logan, P Harrison, A Vasilliev, M Borins, F Paterson
  \textit{FedDev Ontario?s ARC Initiatives OCAD University Project \#1 Haptic holography},
  NIME Proceedings,
  2012.

\end{thebibliography}

% \section{Skills}
% \cvitem{Programming Languages}{JavaScript, C, C++, Python}
% \cvitem{Web Technologies}{Node.js, npm, HTML5, CSS, various preprocessors for both HTML / CSS, aws, gcp}
% \cvitem{Web Frameworks / Libraries}{Angular, Famous, jQuery, browserify}
% \cvitem{Systems}{unix, docker, bash, vim, git, Shell Scripting, make, cmake}
% \cvitem{Prototyping}{3D Printing, CNC-Milling, Laser Cutting, Wood/Metal/Plastics shop experience}
% \cvitem{DSP}{rtaudio, Faust, Matlab, web-audio, Max/MSP, PureData, Chuck}
% \cvitem{Project Contributor}{Node.js, npm, Yeoman, Homebrew, Flocking, OSCeleton, Https Everywhere, monome, faust}
\end{document}
